Age-related changes in plant growth and traits

### 2016-05-17 scripts/Accessory_figs_20160218.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

@@

#Table 2 showing seedcost breakdown into components, by species
```{r}
prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
prop_seedcosts_spp$species <- labels.spp.full()
prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
```

#Figure 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

@@

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
#abline(slopes$groupsummary["Int"][[1]],1,col="red")
abline(0,1,col="red")
words.bottom.right.logxy(mod)

@@

plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
slopes <- sma(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal","total postpollen")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
```
plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,col=col.spp(species),log="x")

>>>>

#SummarySpp[["mean"]]$embryo_endo_West1990 <- c(22.246,3.6828,1.0961,0.02,31.234,10.961,12.446,0.29716,0.8064,12.328,3.2274,1.7127,1.1583,1.274)
SummarySpp[["mean"]]$embryo_endo_West1990 <- c(120,3.6828,0.8,0.02,31.234,10.961,12.446,0.29716,0.8064,12.328,3.2274,1.7127,0.72,1.274)
SummarySpp[["mean"]]$provisioning2 <- SummarySpp[["mean"]]$postpollen_all_per_seed - SummarySpp[["mean"]]$embryo_endo_West1990

@@

#Table 2 showing seedcost breakdown into components, by species
```{r}
prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
prop_seedcosts_spp$species <- labels.spp.full()
prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
```
$embryo_endo_West1990

#Figure 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_seed_size_acc_cost_correlations.wmf", height=5, width=15)
plot

@@

plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
dev.off()
```

#Figure 3 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure03_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
plot

plot(accessory_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
words.top.left.logxy(mod)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(prepollencosts~embryo_endo_West1990,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(prepollencosts)~log10(embryo_endo_West1990),SummarySpp[["mean"]])
words.top.left.logxy(mod)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)

plot(postpollen_all_per_seed~embryo_endo_West1990,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_West1990),SummarySpp[["mean"]])
words.top.left.logxy(mod)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)

@@

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
#abline(0,1,col="red")
words.bottom.right.logxy(mod)

@@

plot(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
#extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
slopes <- sma(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

# plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
# words.top.left.logxy(mod)
# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
# slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],1,col="red")
# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
```

#Table 3 v2. Slopes for various embryo size by acc cost regressions
```{r}
par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
options(scipen = 5)

plot(accessory_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(accessory_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
#abline(0,1,col="red")
words.bottom.right.logxy(mod)

plot(prepollencosts ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollencosts) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
slopes <- sma(prepollencosts ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(failure_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(failure_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
#extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
slopes <- sma(failure_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(prepollen_all_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollen_all_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
slopes <- sma(prepollen_all_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

# plot(postpollen_aborted_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
# words.top.left.logxy(mod)
# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],1,col="red")
# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

SummarySpp[["mean"]]$provisioning2 <- SummarySpp[["mean"]]$postpollen_all_per_seed - SummarySpp[["mean"]]$embryo_endo_West1990
plot(provisioning2 ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(provisioning2) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
slopes <- sma(provisioning2 ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

slopes <- sma(postpollen_all_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_embryo_endo_West1990_slopes.csv",row.names=FALSE)
```
